---
title:  |
        | Financial Incentives and Health Care Provision: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
author:
  - Danilo Freire[^freire]
  - Umberto Mignozzetti[^mignozzetti]
date: \today
thanks: "We thank Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Guisela Pereira, Adam Przeworski, Catarina Roman, David Skarbek, Denis Stukal, Marcos Tourinho, Scott Tyson, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments. Special thanks to XXXX for their excellent research assistance. Replication materials are available at <http://github.com/danilofreire/incentives-health-care>."
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: unsrtnat
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: template.latex
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)

# Install required packages
pkgs <- c("tidyverse", "magrittr", "lmtest",
          "estimatr", "sandwich", "stargazer",
          "gridExtra", "WeightIt", "robustHD",
          "kableExtra", "lfe", "fixest")

installIfNot <- function(x) {
  if(x %in% rownames(installed.packages()) == FALSE)
    install.packages(x, dependencies = T)
}
invisible(lapply(pkgs, installIfNot))

# Load packages
invisible(lapply(pkgs, require, character.only = T))
rm(pkgs, installIfNot, r)

# Load data
load("../data/incentives_healthcare.RData")
```

[^freire]: Independent Researcher,
[`danilofreire@gmail.com`](mailto:danilofreire@gmail.com),
<http://danilofreire.github.io>.

[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods
Department, Emory University, 532 North Kilgo Circle, 4^th^ Floor, Atlanta, GA
30322, USA,
[`umberto.mignozzetti@emory.edu`](mailto:umberto.mignozzetti@emory.edu),
<http://umbertomig.com>. Corresponding author.

\newpage

\begin{abstract}

\footnotesize

\noindent \textbf{Background}. Mosquito control is the primary means to reduce
\textit{Aedes aegypti} infections worldwide. However, programmes such as
insecticide spraying and elimination of breeding sites are conducted
inconsistently in many developing nations. Recent studies indicate that
financial incentives may increase the productivity of health personnel, yet
there is little evidence about the impact of monetary rewards on \textit{A.
aegypti}-reduction strategies. We evaluated whether individual and collective
financial incentives improve the performance of healthcare workers fighting
\textit{A. aegypti}, as well as their effect on city-level numbers of dengue
hospitalisations.

\noindent \textbf{Methodology/Principal findings}. We hired and trained
subjects to visit households, find \textit{A. aegypti} breeding sites, and kill
mosquito larvae in the city of Rio Verde, Brazil. In our randomised field
trial, we provided individual and team bonuses to two treatment groups, and
offered a flat compensation to the control group for completing their tasks.
Financial rewards increased the number of cleaned breeding sites in both
treatment groups (individual and team bonuses) and the collective treatment
also improved larvae extermination. The intervention lowered dengue
hospitalisations in 10.3\%, but the result was not consistent across all model
specifications.

\noindent \textbf{Conclusions/Significance}. \textit{A. aegypti} control
programmes may benefit from alternative compensation schemes, specially when
provided to teams. For this strategy to succeed, financial incentives have to
be distributed widely as their aggregate effect is limited. More research is
needed to assess whether higher worker productivity decreases dengue
hospitalisations.

\end{abstract}

\renewcommand{\abstractname}{Author Summary}
\begin{abstract}

\footnotesize

\noindent Diseases transmitted by the \textit{Aedes aegypti} mosquito, such as
chikungunya, dengue, yellow fever, and Zika, continue to kill thousands of
people per year. As there are no safe vaccines for many of these infections,
insecticide spraying and breeding site cleaning are the best means to fight the
mosquito. In several developing countries, which host the majority of
\textit{A. aegypti} infections, anti-mosquito campaigns are carried out
inconsistently, thus it is crucial to find ways to improve the productivity of
healthcare workers in charge of these tasks. We designed a randomised field
experiment that provided individual and collective financial incentives to
healthcare agents in a Brazilian city and tested the effect of monetary rewards
on their productivity and on the number of dengue hospitalisations. We find
that financial bonuses improved the number of cleaned breeding sites in both
treatment groups (individual and team incentives) and that the collective
treatment also improved larvae extermination. The impact of our treatment on
city-level hospitalisations was not consistent across all specifications. In
sum, financial incentives may be used to boost field productivity in
anti-\textit{A. aegypti} programmes, but we suggest that further research is
required to evaluate how healthcare worker productivy impacts city-level
disease outcomes.

\vspace{.3cm} 
\noindent \textbf{Keywords}: Aedes aegypti, dengue, financial
incentives, mosquito control, preventive health care, randomised field
experiment, worker productivity 
\end{abstract}

\normalsize

\newpage
# Introduction
\label{sec:intro}

The *Aedes aegypti* mosquito is the major worldwide vector of several arboviral
diseases, including dengue, yellow fever, Zika, and chikungunya
[@burt2012chikungunya; @jansen2010dengue; @leta2018global;
@thangamani2016vertical]. Over the past 30 years, arboviral incidence has
increased exponentially, with estimates suggesting that dengue is endemic in
around 100 countries and causes 400 million infections and 22 thousands deaths
each year [@bhatt2013global; @cdc2020dengue]. Since there are no safe vaccines
for most *Aedes*-transmitted diseases [@world2017dengue], we have seen a number
of dengue and Zika outbreaks in Asia, the Caribbean, South America, and the
United States [@carlson2016ecological; @leta2018global]. Chikungunya virus,
previously endemic only to Africa, has already been reported in every region of
the world [@grandadam2011chikungunya; @kraemer2015global; @mayer2017emergence].

Mosquito control is the primary strategy to prevent *Aedes*-borne infections
[@beatty2010best; @eisen2009proactive]. The World Health Organization
recommends the elimination of containers and the use of insecticide to reduce
vector breeding, specially in settings where human-vector contacts are
frequent, such as schools, hospitals, and workplaces [@WHO2012global;
@world2020denguecontrol]. However, breeding site cleaning and insecticide
spraying are labour-intensive processes, and they are often carried out
inconsistently in developing countries [@paz2015dengue; @siddiqui2016use;
@WHO2012global]. In this regard, improving the performance of those responsible
for mosquito control is essential to the effectiveness of anti-*Aedes*
programmes.

Research shows that financial incentives may increase the productivity of
health care workers [@clemens2014physicians; @muthmainnah2017improving;
@ulrich2005does]. Nevertheless, systematic reviews indicate that the
generalisability of the available evidence is limited due to methodological
shortcomings, as several studies suffer from selection bias and inadequate
experimental blinding [@bassani2013financial; @flodgren2011overview;
@scott2011effect]. Moreover, it remains unclear which rewarding schemes have a
stronger effect on health care worker performance [@fainman2020design], and
whether monetary incentives have a sustained effect on patient outcomes
[@jha2012long; @langdown2014use].

In this paper, we explore how financial incentives affect the productivity of
health care personnel involved in *A. aegypti* control and how they impact
dengue hospitalisations. We run a randomised field experiment in the city of
Rio Verde, Brazil, which has experienced a peak in dengue infections in the
last years. We hired and trained teams of health care workers to perform
simplified procedures designed to exterminate *A. aegypti* breeding sites. Our
experiment consisted of two treatment arms plus a control condition. We offered
individual or collective bonuses to those allocated in the two treatment
groups, while the control group received a fixed compensation for completing
their tasks. We then measured how the different reward schemes affect the
number of breeding sites discovered, larvae exterminated, and city-level dengue
incidence.

We find that monetary rewards increase the number of cleaned breeding sites in
both treatment conditions (individual and team bonuses), and that collective
financial incentives also improve larvae extermination. Our results show that
the control group has a high number of houses visited in less than two minutes
apart from each other, which suggests that workers may cheat in the absence of
monetary incentives. When we combine both treatments, we also find that the
intervention decreases dengue incidence in 10.3%, but the results are not
robust. In summary, we provide experimental evidence that performance bonuses
enhance public service delivery and that small financial incentives may improve
patient outcomes and reduce hospitalisations in *Aedes*-endemic countries.

# Methods
\label{sec:methods}

We conducted a randomised field trial in Rio Verde, a municipality in the
Brazilian Midwestern state of Goiás. In 2017, Rio Verde had 229,000 inhabitants
and 1,156 confirmed dengue cases, one of highest counts in Goiás
[@goias2020]. We used Facebook advertisements to recruit potential
participants. The advertisements directed applicants to Google Forms, where we
asked for their contact information. We sent a pre-treatment demographic survey
to every applicant who provided a valid email address. At this stage, we
excluded all individuals under 18 years old and invited the remaining
applicants to our training session, which we ran on the 4^th^ of May, 2018. The
meeting involved a lecture on *A. aegypti* vector biology and practical
instructions on how to find and exterminate mosquito breeding sites. Those who
did not attend the session were also excluded from the study.

Table \ref{tab:covbal} displays the attrition and covariate balance tests for
our experiment, and the territorial assignment before and after applying
propensity score matching [@rosenbaum1985constructing] on census tract
characteristics. We observe no significant differences regarding attrition
rates, indicating that the treatment was correctly randomised. Participant
demographics are also similar across all groups, thus the matching technique
successfully balanced the territorial assignment.

\begin{table}[ht] \centering
\small
  \caption{Covariate Balance on Individual Characteristics}
  \label{tab:covbal}
\begin{tabular}{@{\extracolsep{5pt}} lcccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
Variable & Attrition & Control & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex]
& & \multicolumn{5}{l}{Panel A: Attrition Pattern Test} \\
\hline \\[-1.8ex]
```{r, echo = FALSE, cache=TRUE, results='asis'}
tabcov <- data.frame()
pretreat$assign2 <- ifelse(is.na(pretreat$assignment)|
                             pretreat$participating!='Participating',
                           'Attrition', pretreat$assignment)
pretreat$assign2 <- factor(pretreat$assign2, levels = c('Attrition',
                                                        'No bonus',
                                                        'Individual',
                                                        'Collective'))
x = tapply(pretreat$Age,
           pretreat$assign2,
           mean)
y = summary(aov(Age~assign2,
                data = pretreat))
tab <- data.frame(Var = 'Age',
                  `Atrition` = round(x[1],2),
                  `NoBonus` = round(x[2],2),
                  `Individual` = round(x[3],2),
                  `Collective` = round(x[4],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
x = tapply(pretreat$Female,
           pretreat$assign2,
           mean)
y = summary(aov(Female~assign2,
                data = pretreat))
tab <- data.frame(Var = 'Female',
                  `Atrition` = round(x[1],2),
                  `NoBonus` = round(x[2],2),
                  `Individual` = round(x[3],2),
                  `Collective` = round(x[4],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
x = tapply(pretreat$HasVehicle,
           pretreat$assign2,
           mean)
y = summary(aov(HasVehicle~assign2, data = pretreat))
tab <- data.frame(Var = 'Has Vehicle',
                  `Atrition` = round(x[1],2),
                  `NoBonus` = round(x[2],2),
                  `Individual` = round(x[3],2),
                  `Collective` = round(x[4],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
x = round(tapply(rep(1, length(pretreat$assign2)),
                 pretreat$assign2,
                 sum), digits = 0)
tab <- data.frame(Var = 'N',
                  `Atrition` = round(x[1],2),
                  `NoBonus` = round(x[2],2),
                  `Individual` = round(x[3],2),
                  `Collective` = round(x[4],2),
                  FVal = NA,
                  Pvalue = NA)
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
for (i in 1:dim(tabcov)[1]) {
  s <- paste(tabcov[i,], collapse = ' & ')
  s <- gsub('NA', '', paste(tabcov[i,], collapse = ' & '))
  cat(paste(s, ' \\\\ ', sep = ''), '\n')
}
```
\hline \\[-1.8ex]
\end{tabular}
\begin{tabular}{@{\extracolsep{5pt}} lccccc}
Variable & Control & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex]
& \multicolumn{5}{l}{Panel B: Covariate Balance on Individual Characteristics} \\
\hline \\[-1.8ex]
```{r, echo = FALSE, cache=TRUE, results='asis'}
tabcov <- data.frame()
pretreat$assign3 <- ifelse(is.na(pretreat$assignment)|
                             pretreat$participating!='Participating',
                           NA, pretreat$assignment)
pretreat$assign3 <- factor(pretreat$assign3, levels = c('No bonus',
                                                        'Individual',
                                                        'Collective'))
aux <- filter(pretreat, !is.na(assign3))
# Age
x = tapply(aux$Age,
           aux$assign3,
           mean)
y = summary(aov(Age~assign3,
                data = aux))
tab <- data.frame(Var = 'Age',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Altruism
x = tapply(aux$aboveMedianAltr,
           aux$assign3,
           mean)
y = summary(aov(aboveMedianAltr~assign3,
                data = aux))
tab <- data.frame(Var = 'Altruist',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Religiosity
x = tapply(aux$relig,
           aux$assign3,
           mean)
y = summary(aov(relig~assign3,
                data = aux))
tab <- data.frame(Var = 'Religiosity',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Political Engagement
x = tapply(aux$polengage,
           aux$assign3,
           mean)
y = summary(aov(polengage~assign3,
                data = aux))
tab <- data.frame(Var = 'Pol. Engagement',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Social Engagement
x = tapply(aux$socengage,
           aux$assign3,
           mean)
y = summary(aov(socengage~assign3,
                data = aux))
tab <- data.frame(Var = 'Soc. Engagement',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Above Two Minimum Wage Family
x = tapply(aux$aboveTwoMinWageFam,
           aux$assign3,
           mean)
y = summary(aov(aboveTwoMinWageFam~assign3,
                data = aux))
tab <- data.frame(Var = 'Above Two Min. Wage',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Above Median Facebook popularity
x = tapply(aux$FBpop,
           aux$assign3,
           mean)
y = summary(aov(FBpop~assign3,
                data = aux))
tab <- data.frame(Var = 'Facebook Popularity',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# N
x = round(tapply(rep(1, length(aux$assign3)),
                 aux$assign3,
                 sum), digits = 0)
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
for (i in 1:dim(tabcov)[1]) {
  s <- paste(tabcov[i,], collapse = ' & ')
  s <- gsub('NA', '', paste(tabcov[i,], collapse = ' & '))
  cat(paste(s, ' \\\\ ', sep = ''), '\n')
}
```
\hline \\[-1.8ex]
& \multicolumn{5}{l}{Panel C: Unmatched Covariate Balance on Territorial Assignment} \\
\hline \\[-1.8ex]
```{r, echo = FALSE, cache=TRUE, results='asis'}
## Census Sectors characteristics
tabcov <- data.frame()

# Number of Houses
x = tapply(dfr2$NHouses,
           dfr2$D1,
           mean)
y = summary(aov(NHouses~D1, data = dfr2))
tab <- data.frame(Var = 'Number of Houses',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Age
x = tapply(dfr2$NHouseholds,
           dfr2$D1,
           mean)
y = summary(aov(NHouseholds~D1, data = dfr2))
tab <- data.frame(Var = 'Number of Households',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# AvgHouseholdSize
x = tapply(dfr2$AvgHouseholdSize,
           dfr2$D1,
           mean)
y = summary(aov(AvgHouseholdSize~D1, data = dfr2))
tab <- data.frame(Var = 'Avg. Household Size',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Avg. Income Households
x = tapply(dfr2$logAvgIncomeHousehold,
           dfr2$D1,
           mean)
y = summary(aov(logAvgIncomeHousehold~D1, data = dfr2))
tab <- data.frame(Var = 'Log Avg. Income',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Cases Before
x = tapply(dfr2$plac,
           dfr2$D1,
           mean)
y = summary(aov(plac~D1, data = dfr2))
tab <- data.frame(Var = 'Cases Before Treatment',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
## re-weighting
dfr2$weightsD1 = weightit(D1~NHouses+
                    NHouseholds+AvgHouseholdSize+
                    logAvgIncomeHousehold+plac,
                  data = dfr2, focal = "No bonus",
                  method = 'cbps',
                  estimand = "ATT")$weights

dfr$weightsD1 <- weightit(D1~NHouses+
                    NHouseholds+AvgHouseholdSize+
                    logAvgIncomeHousehold+plac,
                  data = dfr, focal = "Control",
                  method = 'cbps',
                  estimand = "ATT")$weights

dfr$weightsD2 <- weightit(D2~NHouses+
                            NHouseholds+AvgHouseholdSize+
                            logAvgIncomeHousehold+plac,
                          data = dfr, focal = "No intervention",
                          method = 'cbps',
                          estimand = "ATT")$weights
for (i in 1:dim(tabcov)[1]) {
  s <- paste(tabcov[i,], collapse = ' & ')
  s <- gsub('NA', '', paste(tabcov[i,], collapse = ' & '))
  cat(paste(s, ' \\\\ ', sep = ''), '\n')
}
```
\hline \\[-1.8ex]
& \multicolumn{5}{l}{Panel D: Matched Covariate Balance on Territorial Assignment} \\
\hline \\[-1.8ex]
```{r, echo = FALSE, cache=TRUE, results='asis'}
tabcov <- data.frame()
# Number of Houses
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(NHouses, weightsD1),
            .groups = 'drop')
x = x$x
x
y = summary(aov(NHouses~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Number of Houses',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Number of households
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(NHouseholds, weightsD1),
            .groups = 'drop')
x = x$x
y = summary(aov(NHouseholds~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Number of Households',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# AvgHouseholdSize
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(AvgHouseholdSize, weightsD1),
            .groups = 'drop')
x = x$x
y = summary(aov(AvgHouseholdSize~D1, data = dfr2,
                weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Avg. Household Size',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Avg. Income Households
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(logAvgIncomeHousehold, weightsD1),
            .groups = 'drop')
x = x$x
y = summary(aov(logAvgIncomeHousehold~D1, data = dfr2,
                weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Log Avg. Income',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Cases Before
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(plac, weightsD1),
            .groups = 'drop')
x = x$x
y = summary(aov(plac~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Cases Before Treatment',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
for (i in 1:dim(tabcov)[1]) {
  s <- paste(tabcov[i,], collapse = ' & ')
  s <- gsub('NA', '', paste(tabcov[i,], collapse = ' & '))
  cat(paste(s, ' \\\\ ', sep = ''), '\n')
}
```
\hline
Pairs & 29 & 32 & 37 &  &  \\
N & 58 & 64 & 74 &  &  \\
\hline\hline \\[-1.8ex]
\end{tabular}
\end{table}

\normalsize

The intervention took place on the 5^th^ of May, 2018. We randomly assigned
subjects into three groups and directed each group to separate headquarters to
avoid spillovers. In the control group ($n = $ `r as.numeric(table(prodfr$D)[1])`), we told participants that
they would receive a flat payment regardless of their performance (BRL 110 /
USD 25 per subject). In the individual treatment group ($n = $ `r as.numeric(table(prodfr$D)[2])`), we informed
subjects that we would rank each subject separately and double the compensation
for those who performed above the sample median (BRL 220 / USD 50 per subject).
In the collective treatment group ($n = $ `r as.numeric(table(prodfr$D)[3])`), we explained that we would rank
the performance of each group and double the payment for those teams whose
results were higher than the sample median (BRL 220 / USD 50 per subject).
Participants worked in pairs and were aware of other groups, but they did not
know about the different treatment conditions. The teams received a leaflet
with a map of the area they should cover. Each route included around 120 houses
in two or three blocks.

A typical household visit consisted of the following steps. First, participants
rang the doorbell and explained that the municipality had experienced a dengue
fever outbreak. They instructed dwellers on how to lower dengue incidence and
handed them a leaflet with information about dengue prevention practices. Then,
subjects asked whether they were allowed to inspect the resident's house yard.
If granted permission, they entered the household and searched for clean
breeding sites, such as pots filled with clear water, and for recipients
containing larvae. Upon exterminating a breeding site (pouring out the
accumulated water, for example), subjects had to report their task by taking a
photo on their cellphones. When they discovered larvae, participants had to
record a short video showing the larvae before exterminating them. At the end
of each visit, subjects had to take a picture of the household to account for
their presence in the location.

This study evaluates two outcomes. The first outcome is the field productivity
of health care providers. We measure worker productivity by coding cellphone
data collected during the intervention into four indicators: 1) the number of
houses visited; 2) the number of houses visited within less than two minutes;
3) the number of breeding sites removed and cleaned; 4) the number of
exterminated larvae. We analyse the data using ordinary least squares with
robust standard errors [@imbens2016robust]. We estimate the statistical
power of the study assuming a treatment effect of 0.15 standard deviations.

The second outcome of interest is dengue incidence in the municipality of Rio
Verde measured 4, 8, 12, and 16 days after the intervention. The Rio Verde
Mayor's Office provided us with its annual health care report, which contains
the dates and personal information of patients who had dengue fever and
received hospital treatment from January to September 2018. We georeferenced
the home addresses of the patients and compared the incidence map with the
distribution of our intervention. We also compare dengue incidence in each of
the treatment statuses with incidence figures in the control group. In both
models, the unit of analysis is the census tract. We employ a
differences-in-differences estimator to measure the treatment effects
[@angrist2008mostly].

We pre-registered the experiment on the Evidence in Governance and Policy
(EGAP) website (<https://osf.io/6q8vu/>), and received IRB approval from New
York University (IRB-FY2017-17) and Fundação Getulio Vargas (IRB-01/2017). The
funders of this study had no influence over the formulation, organisation,
analysis, and interpretation of the outcomes. Health care workers gave written
consent upon filling the Qualtrics questionnaire. During the intervention, the
occupants of households inspected for breeding sites and larvae gave oral
consent. For more information on the experimental design, sample
characteristics, exclusion criteria, and estimation methods, please refer to
the Supplementary Material.

# Results
\label{sec:results}

We find that financial incentives significantly increase the field productivity
of health care workers fighting *Aedes aegypti*. Subjects in both the
individual and the collective bonus groups locate more mosquito breeding sites
and exterminate more larvae than participants in the control condition. Our
results also show the intervention decreases city-wide levels of dengue
incidence, but the coefficients only reach statistical significance when we
combine the two treatments and contrast them with the control group. Overall,
the findings suggest that monetary payments are an effective method of
improving health worker performance, yet more research is needed to assess
whether higher labour productivity leads to fewer dengue-related
hospitalisations.

## Field Productivity
\label{sub:productivity}

We have four indicators to measure health worker productivity. The first is the
number of houses visited during the intervention. The second indicator is the
number of houses in which the visits lasted for less than two minutes. The
third dependent variable is the number of *A. aegypti* breeding sites removed
and cleaned. Our fourth variable indicates the number of mosquito larvae
exterminated. Table \ref{tab:productivity} summarises the experimental results.

```{r, echo = FALSE, results='asis', warning=FALSE}
## Productivity outcome
mprod <- list()
mprod[[1]] <- lm(nHouse ~ D, data = prodfr)
mprod[[2]] <- lm(nHouseLessTwoMin ~ D, data = prodfr)
mprod[[3]] <- lm(nBreed ~ D, data = prodfr)
mprod[[4]] <- lm(nLarvae ~ D, data = prodfr)
stargazer(mprod[[1]], mprod[[2]],
          mprod[[3]], mprod[[4]],
          se = starprep(mprod[[1]], mprod[[2]],
                        mprod[[3]], mprod[[4]],
                        se_type = "HC1"),
          dep.var.labels = c('\\shortstack{Houses \\\\ Visited}',
                             '\\shortstack{Houses Visited \\\\ in Less than \\\\ Two Minutes}',
                             '\\shortstack{Breeding Sites \\\\ Terminated}',
                             '\\shortstack{Larvae \\\\ Terminated}'),
          keep.stat = c('ser', 'n'),
          notes = c('Robust Standard Errors in parenthesis.'),
          keep = c('DIndividual', 'DCollective'),
          covariate.labels = c('Individual Bonus',
                               'Collective Bonus'),
          title = 'Field Productivity', header = FALSE,
          label = 'tab:productivity')
```

Subjects who received monetary incentives, either alone or in pairs, visited
fewer houses than those who did not earn financial rewards. While the result
seems counter-intuitive, it actually attests the effectiveness of the
treatment. This is because we offered incentives for subjects to exterminate
larvae and find breeding sites, not to visit a greater number of households. As
a result, participants in the two treatment groups did a thorough job in each
household, which explains the lower number of visits during the allotted time.
We find that subjects in the individual and in the collective bonus groups
visited `r round(as.numeric(coef(mprod[[1]])[2]), 3)` (CI: [`r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[2,1]`, `r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[2,2]`]) and `r round(as.numeric(coef(mprod[[1]])[3]), 3)` (CI: [`r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[3,2]`]) households,
respectively.

Our second indicator provides further evidence in favour of our argument. We
see that the two groups which earned performance bonuses spent more time in the
households, as their number of houses visited for less than two minutes is
significantly lower than those of the control condition. On average,
participants in the individual bonus treatment arm visited `r round(as.numeric(coef(mprod[[2]])[2]), 3)` (CI: [`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[2,1]`,
`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[2,2]`]) houses than the control, and those in the collective bonus group visited
`r round(as.numeric(coef(mprod[[2]])[3]), 3)` (CI: [`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[3,2]`]).

Incentivised teams find and clean more breeding sites than non-incentivised
ones. Individually incentivised health workers find `r round(as.numeric(coef(mprod[[3]])[2]), 3)` (CI: [`r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[2,1]`, `r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[2,2]`])
more breeding sites than the non-incentivised control group. The effect for
those in the collective bonus group is `r round(as.numeric(coef(mprod[[3]])[3]), 3)` (CI: [`r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[3,2]`]), slightly
smaller than for the individual treatment.

Teams which received collective bonuses are the most effective in finding
larvae. Subjects who worked in pairs have a `r round(as.numeric(coef(mprod[[4]])[3]*100),1)`% (CI: [`r round(coefci(mprod[[4]], vcov = vcovHC(mprod[[4]], type = "HC1"), level = 0.9), digits=3)[3,1]*100`%, `r round(coefci(mprod[[4]], vcov = vcovHC(mprod[[4]], type = "HC1"), level = 0.9), digits=3)[3,2]*100`%]) higher
likelihood of finding larvae than those in the control group. Locating mosquito
larvae is a difficult task, thus the probability of successfully completing the
task increases when subjects work in teams. Furthermore, our collective bonus
scheme was not excludable within the teams, thus health care workers had an
incentive to cooperate and receive higher rewards.

## Disease Incidence
\label{sub:incidence}

We employ two models to evaluate the effect of monetary incentives on dengue
incidence. The first is a differences-in-differences model that tests
whether the intervention _per se_ had any effect on dengue hospitalisations in
the city of Rio Verde. The second model compares dengue incidence in each of
the treatment statuses with incidence figures in the control group. The unit of
analysis is the census tract. Table \ref{tab:incidence} displays the results
for our first model, in which we measure the impact of our intervention after 4,
8, 12, and 16 weeks. The last column shows how collective incentives compare
with individual bonuses, with the latter considered as the control group.

\vspace{.3cm}

```{r, echo = FALSE, results='asis'}
mod <- list()
mod[[1]] <- felm(ncas4weekwindow ~ Tm2+D+DID|0|0|CensusSectors, data = did_full)
mod[[2]] <- felm(ncas8weekwindow ~ Tm2+D+DID|0|0|CensusSectors, data = did_full)
mod[[3]] <- felm(ncas12weekwindow ~ Tm2+D+DID|0|0|CensusSectors, data = did_full)
mod[[4]] <- felm(ncas ~ Tm2+D+DID|0|0|CensusSectors, data = did_full)
stargazer(mod[[1]], mod[[2]], mod[[3]], mod[[4]],
          dep.var.labels = c('\\shortstack{Four \\\\ Weeks Window}',
                             '\\shortstack{Eight \\\\ Weeks Window}',
                             '\\shortstack{Twelve \\\\ Weeks Window}',
                             '\\shortstack{Sixteen \\\\ Weeks Window}'),
          keep.stat = c('ser', 'n'),
          keep = c('DID'),
          notes = c('Robust standard errors clustered at the census tract level in parentheses.'),
          label = 'tab:incidence',
          covariate.labels = c('Dif-in-Dif'),
          dep.var.caption = "Disease Incidence Before and After Intervention:",
          title = 'Differences-in-Differences Model', header = FALSE)
```

The intervention lowered dengue incidence in `r round(as.numeric(coef(mod[[4]])[4])*100, 1)`% (CI: [`r round(tidy(mod[[4]], conf.level = 0.9, conf.int = T)$conf.low[4]*100, 1)`%, `r round(tidy(mod[[4]], conf.level = 0.9, conf.int = T)$conf.high[4]*100, 1)`%]) if we take
both treatments together and compare them with the control group. The result is
consistent around fewer weeks before and after the intervention, but it does
not reach conventional levels of statistical significance. This suggests that
the treatment effect is probably small.

\vspace{.3cm}

```{r, echo=FALSE, results='asis'}
## Health outcome
moutc <- list()
moutc[[1]] <- lm(nc15dafter ~ D1,
                 data = dfr2, weights = dfr2$weightsD1)
moutc[[2]] <- lm(nc30dafter ~ D1,
                 data = dfr2, weights = dfr2$weightsD1)
moutc[[3]] <- lm(nc60dafter ~ D1,
                 data = dfr2, weights = dfr2$weightsD1)
moutc[[4]] <- lm(nc90dafter ~ D1,
                 data = dfr2, weights = dfr2$weightsD1)
moutc[[5]] <- lm(nc30to60dafter ~ D1,
                 data = dfr2, weights = dfr2$weightsD1)
moutc[[6]] <- lm(plac ~ D1,
                 data = dfr2, weights = dfr2$weightsD1)

stargazer(moutc[[6]], moutc[[1]], moutc[[2]],
          moutc[[3]], moutc[[4]], moutc[[5]],
          se = starprep(moutc[[6]], moutc[[1]],
                        moutc[[2]], moutc[[3]],
                        moutc[[4]], moutc[[5]],
                        se_type = "HC1"),
          dep.var.labels = c('\\shortstack{Before \\\\ Int.}',
                             '\\shortstack{Fifteen \\\\ Days \\\\ After Int.}',
                             '\\shortstack{Thirty \\\\ Days \\\\ After Int.}',
                             '\\shortstack{Sixty \\\\ Days \\\\ After Int.}',
                             '\\shortstack{Ninety \\\\ Days \\\\ After Int.}',
                             '\\shortstack{Btw. Thirty \\\\ \\& Sixty Days \\\\ After Int.}'), label = 'tab:census',
          keep.stat = c('ser', 'n'),
          keep = c('D1Individual', 'D1Collective'),
          covariate.labels = c('Individual Bonus',
                               'Collective Bonus'),
          dep.var.caption = "Number of Reported Hospital Cases:",
          title = 'Disease Incidence', header = FALSE,
          font.size = 'small')
```

In our second model, we measure the effect of reward schemes on the number of
hospitalisations per census tract. Table \ref{tab:census} shows hospitalisation
counts before the intervention, and then 15, 30, 60, 90, and between 30 to 60
days after the treatment.

Compared to the control group, neither treatment had an impact on disease
incidence in the Rio Verde census tracts. The treatment effect is not
statistically different from zero in any model specification. Yet, the
coefficients are negative, what indicates that should an impact have occurred,
the intervention would have lowered dengue incidence in the treated areas.

# Discussion
\label{sec:discussion}

We show that monetary incentives increase the productivity of community health
care workers in Brazil. We contrast a control group (which received a flat
performance fee) with two treatment groups, one which received an individual
performance bonus, and second one that received a collective performance
incentive. We find that both treatments increase the number of breeding sites
encountered, and that collective incentives outperform individual performance
rewards when the task is more laborious and excludable (exterminating larvae).
Lastly, the control group presented a high incidence of houses visited in less
than two minutes apart from each other, which suggests that the workers may
not carry their tasks as intended in the absence of incentives. In a nutshell,
monetary incentives work.

Our conclusions are consistent with the results of comparable studies conducted
in other settings, such as education [@duflo2012incentives] and private firms
[@bandiera2013team]. They also provide further evidence that incentivising team
work is more effective for labour-intensive tasks, which opens a new avenue for
research in preventive health care.

Regarding the effect of incentives on city-level dengue incidence, we find only
mixed results. Why did the treatment not work as we planned? We believe the
treatment was not strong enough. Our treatment probably did not cover enough
areas to ensure there was no mosquitos around the assigned blocks. As mosquitos
can travel for long distances, the treatment might not have been sufficient.
Also, Rio Verde had significant rates of dengue incidence during our
experiment, reaching 3,411 reported infections from January to September 2018
[@goias2020]. Therefore, maybe the treatment works only when applied for
longer periods of time or in more neighbourhoods.

In this respect, our study suggests is that even though health care workers may
be motivated, their efforts do not necessarily lead to a reduction in mosquito
infections. Higher field productivity does not guarantee that the *Aedes
aegypti* can be eradicated. To our knowledge, we are one of the first studies
to highlight this issue. Future research may explore the reasons why this is
the case and if the disconnect between the two can also be identified in other
areas.

## Limitations
\label{sub:limitations}

The study has several limitations. First, we ran our experiment for a small
period of time and in a particular Brazilian city, thus the findings may not
generalise to other locations. Second, our experiment needed a longer and wider
coverage to measure whether the treatment has a significant impact on dengue
incidence, as the effect seems smaller than expected. Third, we included a
post-treatment adjustment to ensure the balance of our territorial variables.
Although using matching estimators to improve balance is in line with the best
statistical practices, it requires additional assumptions. Finally, the
experiment only measures the impact of financial rewards on worker performance,
and it does not assess the effect of non-monetary incentives, such as
motivational messages or constant feedback, which may be useful alternatives in
jurisdictions where legal or financial constraints prevent the government from
distributing financial bonuses to civil servants.

## Public Health Implications
\label{sub:implications}

The experiment has important lessons for policy-making. *Aedes aegypti*-borne
diseases are a significant public health concern, especially in developing
nations. Results of this study indicate that monetary rewards play a major role
in motivating civil servants, and that peer incentives are more cost-effective
than individual bonuses. Finally, the article shows anti-mosquito campaigns
require a sustained effort to guarantee their success, and we still have no
robust evidence that worker productivity alone is sufficient to reduce dengue
infections.

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}
